---
title: 'Blog assignment 1: Totalitarianism, authoritarianism, and competitive authoritarianism'
output: pdf_document
---

## For people whose IDs end in 0 and 9, due March 10 and March 14 respectively

The readings for this assignment have to do with the distinction between totalitarian, authoritarian, and competitive authoritarian regimes. The basic readings contain the key concepts we will be using in the course, though they are not necessarily the easiest to read. The additional readings are often more fun, but they need only concern you if it is your turn to do an explanatory blog post. They are a mixture of theoretical readings and case studies. Some are long and difficult; others are short and easy. If it is your turn to do an EBP, you should select one reading (one of the basic readings or one of the additional readings, it doesn't matter - your choice) and write a post about it for [the course blog](http://politicalpathologies.blogspot.com).

Your explanatory blog post should 1) summarize the reading *in your own words* 2) put it into some sort of context (which may require that you read further or find additional resources) and (if possible) 3) attempt to evaluate its claims. 

With respect to 1), remember you are writing a blog post to be read by your classmates, not some boring slapdash essay to be read only by your lecturer (me). Make use of the possibilities of the medium to explain the key points to your peers! Other students in previous years in this course have made good use of video, pictures, and other media to explain difficult content; check some of the things that other people have done in the blog to get some ideas. Nevertheless, remember to use *your own words* and to link to your sources if you make controversial claims; if you do not know how to create a link in the blog, I'm happy to show you.

With respect to 2), you should try not just to summarize the article you've chosen, but to try to provide some context. Is there some broader question addressed by the article you've chosen? Does the article or chapter take a controversial position, or does it summarize the scholarly consensus? Do other scholars seem to agree or disagree with the article you've chosen? 

With respect to 3), you may not be able to fully evaluate the claims in the article or chapter you chose (that may require lots of knowledge you don't yet have, especially if, for example, the article uses statistic or archival sources), but you can still ask yourself such questions as whether the article's methods make sense, its sources seem reliable, its interpretations appear accurate, and its conclusions seem reasonable. You may need to do some additional research to do this well - e.g., try to find out whether other people disagree with the author and why.

Your job, ultimately, is to *explain* your chosen reading to the class. But though you can choose whichever reading you want for your EBP, *all* of the readings should be summarized by the end of the week or class points might be lost. This requires coordination! If, for example, everyone chooses to do their EBP on the one article that is 2 pages long, you may do well, but the class will suffer; you should try to figure out how to avoid this outcome. Moreover, collectively, the EBPs should try (together - not your post specifically, but all of them as a whole) to answer some basic questions:

* What are totalitarian regimes? What are authoritarian regimes?
* What are the key characteristics of totalitarian regimes? How do they differ from authoritarian regimes?
* What are some totalitarian regimes? What are some authoritarian regimes?
* How do totalitarian regimes emerge? How do they end?
* What are some of the controversies about totalitarianism?
* Is the concept of totalitarianism still relevant today? Why or why not?
* What are competitive authoritarian regimes? Why are they important?
* How should we distinguish authoritarian, competitive authoritarian, and democratic regimes? Does it matter where we draw these lines?
* How do competitive authoritarian regimes emerge? How do they end?

The following people (IDs ending in 0) should submit their post to the blog on Tuesday 10 March 

```{r, peopleWithIDsEndingIn0, echo=FALSE, message=FALSE}
library(dplyr)
BB <- read.csv(dir(pattern="gc_2015"),fileEncoding ="UTF-8-BOM") %>% 
  filter(Availability == "Yes") %>%
  #mutate(Last.Name = paste0(abbreviate(Last.Name,minlength=1,strict=TRUE),".")) %>%
  select(Last.Name,First.Name,Student.ID)

BB %>% filter(Student.ID %% 10 == 0)

```

The following people (IDs ending in 9) should submit their post to the blog on Friday 14 March.

```{r, peopleWithIDsEndingIn9, echo=FALSE}

BB %>% filter(Student.ID %% 10 == 9)

```

Enjoy!

#### Basic readings:

1.	Linz, Juan J. 2000. Totalitarian and Authoritarian Regimes. Boulder, CO: Lynne Rienner Publishers. Chapter 2: Totalitarianism. Pp. 65-142. 

Unfortunately most work on totalitarianism came in big books; outside of Wikipedia, there are few short treatments of the concept. This piece on totalitarianism by Juan Linz is extremely comprehensive (Linz had an encyclopedic knowledge of the politics of many countries), but it is also quite dry and very long. It also assumes some knowledge of history you may not have. If you run into difficulties reading it, try to at least get the basic points of the piece. Consider, in particular, the following questions: What are the key characteristics of totalitarianism? Which characteristics are essential to the concept, and which are not? What are some examples of totalitarian regimes? How did their politics differ from the politics of other non-democratic regimes? 

2.	Levitsky, Steven, and Lucan Way. 2010. Competitive Authoritarianism: Hybrid Regimes after the Cold War. New York: Cambridge University Press. Chapter 1, pp. 3-36. 

Levitsky and Way coined the term "competitive authoritarianism" in [an earlier article](http://muse.jhu.edu/journals/journal_of_democracy/v013/13.2levitsky.html), which you may find useful to peruse if this piece proves too heavy. This is the introduction of a book discussing all examples of competitive authoritarianism that emerged in the 1990s. Levitsky and Way have a distinctive theory of competitive authoritarianism: what it is, how it emerges, and how competitive authoritarian regimes become democratized. Consider, in particular, what distinguishes such regimes from democracies and from other authoritarian regimes, as well as what they say about the factors that promote their stability or democratization. 

### Additional readings

The following readings need to be covered in EBPs by people whose IDs end in 0 (Tuesday) or 9 (Friday). See here for more details.

1.	Rummel, Rudolph J. 1995. Democracy, Power, Genocide, and Mass Murder. The Journal of Conflict Resolution 39 (1): 3-26. http://www.jstor.org/stable/174320 Argues that totalitarian regimes have been responsible for the main cases of genocide and politicide in the world. 

2. Kershaw, Ian. 1993. ‘Working Towards the Führer.’ Reflections on the Nature of the Hitler Dictatorship. Contemporary European History 2 (02): 103-118. http://www.jstor.org/stable/20081474

3.	Sondrol, Paul C. 1991. Totalitarian and Authoritarian Dictators: A Comparison of Fidel Castro and Alfredo Stroessner. Journal of Latin American Studies 23 (03): 599-620. http://dx.doi.org/10.1017/S0022216X00015868 An attempt to distinguish between authoritarian and totalitarian dictators in two Latin American cases.

4. Havel, Vaclav (1992). “The Power of the Powerless” In Open Letters, pp. 125-153. New York: Vintage Books (available here, http://vaclavhavel.cz/showtrans.php?cat=eseje&val=2_aj_eseje.html&typ=HTML). Havel was a Czechoslovak dissident who eventually (after the Velvet revolution) became president of Czechoslovakia. This was written from prison - the "greengrocer parable" is still a great way of understanding totalitarianism. 

5. Blaydes, Lisa. 2010. Elections and Distributive Politics in Mubarak's Egypt. Cambridge University Press. Chapter 1 is a good description of authoritarianism in Egypt. Was Egypt a competitive authoritarian regime, or just plain authoritarian?

6.  Magaloni, Beatriz. 2006. Voting for Autocracy: Hegemonic Party Survival and its Demise in Mexico. Cambridge University Press. Chapter 1 describes a theory of how elections can help sustain authoritarianism, with a particular focus on Mexico. 

7.	Mainwaring, Scott. 2012. "From Representative Democracy to Participatory Competitive Authoritarianism: Hugo Chávez and Venezuelan Politics." Perspectives on Politics no. 10:955-967. http://dx.doi.org/10.1017/s1537592712002629 The Chavez regime in Venezuela has been the object of much controversy. Was it/is it/did it become authoritarian at some point since the moment Chavez came to power in 1997? Why might some people think the Chavez regime became "competitive authoritarian" at some point? Useful for our "mock trial" later in the course; also contains some discussion of how the Chavez regime emerged.

8.	Levitsky, Steven, and James Loxton. 2013. Populism and competitive authoritarianism in the Andes. Democratization 20 (1): 107-136. http://dx.doi.org/10.1080/13510347.2013.738864 A broader look at the intersection between populism and competitive authoritarianism in Latin America.

9.	Krastev, Ivan, and Stephen Holmes. 2012. "An Autopsy of Managed Democracy." Journal of Democracy no. 23 (3):33-45. http://muse.jhu.edu/journals/journal_of_democracy/v023/23.3.krastev.html Competitive authoritarianism in Russia. What are elections for in Russia? With some fun quotes. This more popular piece by Krastev is also thought-provoking: "Is China more democratic than Russia?" http://www.opendemocracy.net/odrussia/ivan-krastev/is-china-more-democratic-than-russia

10. Kendall-Taylor, Andrea, and Erica Frantz. 2015. Mimicking Democracy to Prolong Autocracies. The Washington Quarterly 37 (4): 71-84. http://dx.doi.org/10.1080/0163660X.2014.1002155 Why might the use of "democratic" facades help prolong authoritarianism?
